### 2022-03-29 ehoh2/ehoh2.tex
concl
more

@@

A term can be $\beta$-reduced as follows: When a cell of the
form $ \internalat(\internallam(\db{0}, s),t)$ is encountered, the field
\texttt{binding} (normally used to record the substitution for a free variable) of the
cell $\db{0}$ is set to $t$. Then $s$ is traversed to instantiate every
loose occurrence of $\db{0}$ in $s$ with \texttt{binding}, whose loosely
bound De Bruijn indices are shifted by the number of $\lambda$ binders above
the occurrence of $\db{0}$ in $s$ \cite{fk-01-deBruijn}. Next, the same
procedure is performed on the resulting term and its subterms, in
leftmost outermost fashion.

@@

  In this section, we try to answer two questions about \ehohii{}: \emph{How does
  \ehohii{} compare against other higher-order provers (including Ehoh)?} \emph{Does
  \ehohii{} introduce any overhead compared with Ehoh?} To answer
  these questions, we ran provers on problems from the TPTP library \cite{gs-17-tptp} and on
  benchmarks generated by Sledgehammer (SH) \cite{pb-12-sh}.
  The experiments were carried out on StarExec Miami
  \cite{sst-14-starexec} nodes equipped with Intel Xeon E5-2620 v4 CPU clocked at
  2.10~GHz. For the TPTP part, we used the CASC-28\footnote{\url{http://www.tptp.org/CASC/28/}} time limits:\ 120~s
  wall-clock and 960~s CPU. For SH benchmarks and to answer the other question, we used Sledgehammer's
  default time limit:\ 30~s wall-clock and CPU.

>>>>

\authors{Joint work with\\
Jasmin~Blanchette and Stephan~Schulz}

@@

A term can be $\beta$-reduced as follows: When a cell of the
form $ \internalat(\internallam(\db{0}, s),t)$ is encountered, the field
\texttt{binding} (normally used to record the substitution for a free variable) of the
cell $\db{0}$ is set to $t$. Then $s$ is traversed to instantiate every
loose occurrence of $\db{0}$ in $s$ with \texttt{binding}, whose loose
bound De Bruijn indices are shifted by the number of $\lambda$ binders above
the occurrence of $\db{0}$ in $s$ \cite{fk-01-deBruijn}. Next, the same
procedure is performed on the resulting term and its subterms, in
leftmost outermost fashion.

@@

  In this section, we try to answer two questions about \ehohii{}: \emph{How does
  \ehohii{} compare against other higher-order provers (including Ehoh)?} \emph{Does
  \ehohii{} introduce any overhead compared with Ehoh?} To answer
  these questions, we ran provers on problems from the TPTP library \cite{gs-17-tptp} and on
  benchmarks generated by Sledgehammer (SH) \cite{pb-12-sh}.
  The experiments were carried out on StarExec Miami
  \cite{sst-14-starexec} nodes equipped with Intel Xeon E5-2620 v4 CPU clocked at
  2.10~GHz. For the TPTP part, we used the CASC-28\footnote{\url{http://www.tptp.org/CASC/28/}} time limits:\ 120~s
  wall-clock and 960~s CPU. For SH benchmarks and to answer the other question, we used Sledgehammer's
  default time limit:\ 30~s wall-clock and CPU.  The raw evaluation data is available online\footnote{\url{https://doi.org/10.5281/zenodo.6389849}}.
